\vspace*{\fill}
\begin{center}

% {\huge Computational Perspectives on Transcription Regulation During (Evolutionary-)Development}

{\huge Computational Perspectives on Transcription Regulation Throughout Evolution and Development}

\vspace{1cm}

\textbf{{\large Proefschrift}}

\vspace{1cm}

ter verkrijging van de graad van doctor aan de Radboud Universiteit Nijmegen op gezag van de recor magnificus prof. dr. J.M. Sanders, volgens besluit van het college voor promoties in het openbaar te verdedigen op

\vspace{1cm}

SOMEDAY 2024

\vspace{1cm}

om 12:00 precies

\vspace{1cm}

door

\vspace{1cm}

\textbf{Maarten van der Sande}

geboren op 13 augustus 1993

te Renkum, Nederland

\end{center}
\vspace*{\fill}

\newpage

\noindent
\textbf{{\large Colophon}}

\noindent
\textbf{Computational Perspectives on Transcription Regulation Throughout Evolution and Development}

\noindent
etc.

\newpage

\vspace*{\fill}

{\raggedleft\vfill\itshape\Longstack[l]{%
  ``The first step is to measure whatever can be easily measured. \\
  The second step is to disregard that which can't easily be \\
  measured or given a quantitative value. The third step is to \\ 
  presume that what can't be measured easily isn't that \\
  important. The fourth step is to say what can't be easily \\
  measured, doesn't exist. This is suicide.''\\
}\\}
\hspace*{\fill} - Daniel Yankelovich

\newpage

{\parindent0pt
\textbf{Promotor}:\newline
- Prof. dr. G. J. C. Veenstra
\vspace{0.5cm}

\textbf{Copromotor}:\newline
- Dr. S. J. van Heeringen
\vspace{0.5cm}

\textbf{Manuscript committee}:\newline
- Prof. dr. M. A. Huijnen \newline
- Prof. dr. C. Gilissen \newline
- Prof. dr. M. K. Richardson \newline
}
\newpage

% table of content
\setcounter{tocdepth}{0}
\tableofcontents
