\section{List of Publications}

PubPeer comment on \textit{Genomic encoding of transcriptional burst kinetics}. \textbf{Maarten van der Sande}. https://pubpeer.com/publications/1AA141AA501FF528C34DFF944CEF8E\#1, 2023.

Genomepy: genes and genomes at your fingertips. S Frölich, \textbf{M van der Sande}, T Schäfers, SJ van Heeringen. Bioinformatics 39 (3), btad119, 2023.

Computational approaches to understand transcription regulation in development. \textbf{M van der Sande}*, S Frölich*, SJ van Heeringen. Biochemical Society Transactions 51 (1), 1-12, 2023.

Qnorm: fast-ish (and correct!) quantile normalization in Python. \textbf{Maarten van der Sande}, SJ van Heeringen
Retinoic acid signaling drives differentiation toward the absorptive lineage in colorectal cancer. RA Wester, \ldots, \textbf{Maarten van der Sande}, \ldots. Iscience 24 (12), 103444, 2021.

ANANSE: An enhancer network-based computational approach for predicting key transcription factors in cell fate determination. Q Xu, G Georgiou, S Frölich, \textbf{M van der Sande}, ..., SJ van Heeringen.Nucleic Acids Research 49 (14), 7966-7985, 2021.

Combinatorial transcription factor activities on open chromatin induce embryonic heterogeneity in vertebrates. AR Bright, \ldots, M Van der Sande, \ldots, SJ van Heeringen. The EMBO Journal 40 (9), e104913, 2021.

Stronger induction of trained immunity by mucosal BCG or MTBVAC vaccination compared to standard intradermal vaccination. MPM Vierboom, ..., \textbf{Maarten van der Sande}, ..., FAW Verreck. Cell Reports Medicine 2 (1), 100185, 2021.

A cell-based boundary model of gastrulation by unipolar ingression in the hydrozoan cnidarian Clytia hemisphaerica. \textbf{M van Der Sande}, Y Kraus, E Houliston, J Kaandorp. Developmental biology 460 (2), 176-186, 2020.
