\section{List of scientific publications}

\noindent
\underline{van der Sande M}*, Frölich S*, Schäfers T, Smits JGA, Snabel RR, Rinzema S, van Heeringen SJ. \textbf{Seq2science: an end-to-end workflow for functional genomics analysis.} PeerJ 11:e16380 \cite{seq2science}
\newline

\noindent
Frölich S, \underline{van der Sande M}, Schäfers T, van Heeringen SJ. \textbf{Genomepy: genes and genomes at your fingertips.} Bioinformatics 39 (3), btad119, 2023. \cite{Frlich2023}
\newline

\noindent
\underline{van der Sande M}*, Frölich* S, van Heeringen SJ. \textbf{Computational approaches to understand transcription regulation in development.} Biochemical Society Transactions 51 (1), 1-12, 2023. \cite{vanderSande2023}
\newline

\noindent
Wester RA, van Voorthuijsen L, Neikes HK, Dijkstra JJ, Lamers LA, Frölich S, \underline{van der Sande M}, Logie C, Lindeboom RGH, Vermeulen M. \textbf{Retinoic acid signaling drives differentiation toward the absorptive lineage in colorectal cancer.} Iscience 24 (12), 103444, 2021. \cite{Wester2021}
\newline

\noindent
Xu Q, Georgiou G, Frölich S, \underline{van der Sande M}, Veenstra GJC, Zhou H, van Heeringen SJ. \textbf{ANANSE: An enhancer network-based computational approach for predicting key transcription factors in cell fate determination.} Nucleic Acids Research 49 (14), 7966-7985, 2021. \cite{Xu_2020}
\newline

\noindent
Bright AR, van Genesen S, Li Q, Grasso A, Frölich S, \underline{van der Sande M}, van Heeringen SJ, Veenstra GJC.
\textbf{Combinatorial transcription factor activities on open chromatin induce embryonic heterogeneity in vertebrates.} The EMBO Journal 40 (9), e104913, 2021. \cite{Bright_2021}
\newline

\noindent
Vierboom MPM, Dijkman K, Sombroek CC, Hofman SO, Boot C, Vervenne RAW, Haanstra KG, \underline{van der Sande M}, van Emst L, Domínguez-Andrés J, Moorlag SJCFM, Kocken CHM, Thole J, Rodriguez E, Puentes E, Martes JHA, van Crevel R, Netea MG, Aguila N, Martin C, Verreck FAW. \textbf{Stronger induction of trained immunity by mucosal BCG or MTBVAC vaccination compared to standard intradermal vaccination.} Cell Reports Medicine 2 (1), 100185, 2021. \cite{Vierboom2021}
\newline

\noindent
\underline{van der Sande M}, Kraus Y, Houliston E, Kaandorp J. \textbf{A cell-based boundary model of gastrulation by unipolar ingression in the hydrozoan cnidarian Clytia hemisphaerica.}  Developmental biology 460 (2), 176-186, 2020. \cite{vanderSande2020}
\newline

\noindent
* These authors contributed equally to this work.

\newpage
\section{List of open-source scientific software contributions}

\noindent
\textbf{Qnorm}: The development of a Python quantile normalization package. The pre-existing implementations did not resolve ties correctly. This implementation is correct, fast-ish, and scales to infinitely large tables. It has been installed 40k+ times through BioConda, and is a requirement of 30+ tools such as Basenji, Gimmemotifs, and TF-COMB.
\newline

\noindent
\textbf{GimmeMotifs}: 17 merged Pull Requests; most notably the addition of the motif2factors command which automatically converts a motif database to any species based on orthology. Moreover, these PRs include numerous bug fixes and documentation improvements.
\newline

\noindent
\textbf{Snakemake}: 9 merged Pull Requests; most notably the addition of automated keyword unpacking and the addition of LockExpection, but also include numerous bug fixes and documentation improvements.
\newline

\noindent
\textbf{MultiQC}: 5 merged Pull Requests; with the addition of the BUStools module, the addition of show/hide buttons, and improvements to the MACS2 module. 
\newline

\noindent
\textbf{BioConda \& Conda-Forge}; maintaining 9 packages (seq2science, ngs-tools, kb-python, peaksql, pyseq-align, pretty\_html\_table, qnorm, iteround, and loompy).
\newline

\noindent
\textbf{Pysradb}: 4 merged pull requests; including performance improvement by multithreaded loading, and bug fixes.
\newline

\noindent
\textbf{Snakemake wrappers}. The addition and maintenance of the Genomepy and encode-download wrappers.
\newline

\noindent
\textbf{MACS2}: 1 merged pull request; which adds the option to include more than 2 replicates for peak calling.
\newline

\noindent
\textbf{gffread}: 1 merged pull request; which removes duplicate code.
\newline

\noindent
\textbf{fluff}: 1 merged pull request; fixing a bug concerning not correctly removing temporary files.
\newline

\noindent
\textbf{kbpython}: 1 merged pull request; extending the recognized nucleotides with the full IUPAC code.
\newline

% \begin{itemize}
%     \item GimmeMotifs: 17 merged pull requests with bug fixes, added functionality, and documentation changes.
%     \item Snakemake: 9 merged pull requests with bug fixes, added functionality, and documentation changes.
%     \item MultiQC: 5 merged pull requests with added functionality, added new and updated existing modules.
%     \item BioConda \& Conda-forge:  maintainer of 4 conda-forge and 5 bioconda packages.
%     \item Pysradb: 4 merged pull requests with performance improvements and bug fixes.
%     \item pyfaidx: 2 merged pull requests with added functionality.
%     \item MACS2: 1 merged pull request with added functionality (now accepts 3 or more replicates).
%     \item gffread: 1 merged pull request of code cleanup (code duplication removed).
%     \item fluff: 1 merged pull request of bug fix (temporary files not always removed).
%     \item kbpython: 1 merged pull request of added feature (IUPAC code extension).
%     \item Snakemake wrappers: genomepy and encode downloader
% \end{itemize}

\newpage